Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-01 Tex/Old text/chapters/chapter02.tex
thesis updated text

\subsection{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). The most basic PV system can give supply only in daytime.  For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

@@

\subsubsection{Unregulated standalone PV system with DC load }
Usually this type of system is for low power applications, as defined by \cite{Roy}. The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}. At night hours, the system will not provide any supply because of the absence of the battery.

@@

\subsubsection{Regulated standalone PV system with DC load}
It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}. Usually system with MPPT should have battery; otherwise, extra power will be waste.

@@

\subsubsection{Regulated standalone system with battery and DC load}
Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}.

@@

\subsubsection{Regulated standalone system with battery, AC load}
This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}. This solution has an increase of cost because has more equipments. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units. That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target. \textcolor{red} { Alternative??? Specifically for remote rural areas of developing countries or places where the grid extension is not feasible,}
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the most suitable configuration is the regulated stand-alone system with battery and AC load.

@@

\subsection{Automated Verification }
It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\subsection{Availability of Stand-alone PV Systems}
\label{sec:availability}
%--------------------------------------------------
%Each stand-alone PV system, like any other power systems, has a specific level of availability. This reliability level impacts various issues, as system performance, production, feasibility, and investment. 
The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
The system availability definition depends on how critical the load application is. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable. %As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
%
%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

>>>>

\section{Solar Photovoltaic System }
According to \cite{Roy}, a PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time (in particular cases, in both times). The most basic PV system can give supply only in daytime.  For night hours or rainy days, one needed to have batteries, where power can be stored and used \cite{Gules}.

@@

\subsection{Unregulated standalone PV system with DC load }
Usually this type of system is for low power applications, as defined by \cite{Roy}. The PV system is directly connected to the load without any MPPT controller, as shown at Fig.\ref{fig:unregSPV}. At night hours, the system will not provide any supply because of the absence of the battery.

@@

\subsection{Regulated standalone PV system with DC load}
It is similar to unregulated standalone system with DC load, but the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated by Fig.\ref{fig:regSPV1}. Usually system with MPPT should have battery; otherwise, extra power will be waste.

@@

\subsection{Regulated standalone system with battery and DC load}
Configuration with PV array, battery, MPPT and DC load, as shown in Fig.\ref{fig:regSPV2}. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}.

@@

\subsection{Regulated standalone system with battery, AC load}
This system is similar to the previous one, but here AC load draws the power from PV system and, because of the AC load, an inverter (DC to AC converter) is required, as seen in Fig.\ref{fig:regSPV3}. This solution has an increase of cost because has more equipments. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units. That configuration is the focus of the present thesis since it is the most common nowadays all over the world, when off-grid or isolated regions is the target. \textcolor{red} { Alternative??? Specifically for remote rural areas of developing countries or places where the grid extension is not feasible,}
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the most suitable configuration is the regulated stand-alone system with battery and AC load.

@@

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\subsection{Availability of Stand-alone PV Systems}
\label{sec:availability}
%--------------------------------------------------
%Each stand-alone PV system, like any other power systems, has a specific level of availability. This reliability level impacts various issues, as system performance, production, feasibility, and investment. 
The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
The system availability definition depends on how critical the load application is. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable. %As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
%
%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
/////////////
%\section{Automated Verification }
It is necessary to keep in mind that validation is the process of determining whether a design meets the needs of the user, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations.

//////////////////

Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

### 2019-07-01 Tex/Old text/chapters/chapter03.tex
thesis updated text

The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

@@

 /////////////
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}
%

@@

>>>>

\section{Automated Verification}
The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

@@

 /////////////
 \section{Optimization}
 Algorithm~\ref{alg:opt-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. It was adopted the analytical method of optimization, with LCC economical analysis and power reliability based on the critical period criteria.
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}
%

@@

\section{Assumptions and Premises}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, 
a list of forty equipment from ten different manufacturers was provided 
to the synthesis engine in order to allow the choice of every item 
of PV sizing. Data sheet from each item was necessary to collect 
technical information. Moreover, the price of each item was obtained 
from available quotations in the market, and if the currency was not in US dollars, 
then it was used the exchange rate of the day to convert it to US dollars.

With respect to power reliability, this work will rely on the critical period solar 
energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
The usual way is to use loss of load probability (LOLP) or loss of power 
supply probability (LPSP). However, based on the fact that here we 
are neither considering site characteristics nor the load changes over time, 
which demands historical data, the reliability analysis will be developed only 
by the critical period method of PV sizing.

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: $20$ years;
	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}. This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years). Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
\end{itemize}

On the subject of PV system optimization technique, we will adopt here the intuitive method 
since the average value daily of solar irradiance is used in the mathematical model, 
without considering the battery's state of charge, or even the random nature 
of solar irradiation and meteorological conditions. Therefore, all the computational 
effort will be concentrated in our automated synthesis algorithm.

Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).

Related to off-the-shelf simulation tools only HOMER Pro and Hybrid2 perform off-grid system with battery backup analysis. Additionally, HOMER and RETScreen include economical analysis or even optimization-sensitive analysis. Therefore, in this study, HOMER Pro will be the simulation tool used to compare with our automated synthesis method.  Related to HOMER Pro:

\begin{itemize}
	\item HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER};
	\item HOMER Pro do not have the LCC cost in its reports. However, it has NPC and LCOE. Therefore NPC was used to obtain LCC in order to allow the comparative among tools;
	\item The optimization analysis of HOMER Pro allows to define a load curve and temperature according of data collected automatically from online databases. However, in order to allow a correct comparative, the curve load and the temperature were defined exactly the same as automated synthesis tools;
	\item Battery autonomy is not an parameter that the user can set when using HOMER Pro. The tool will always to meet the user requirement, i.e., the load curve during the $365$ days of the year;
	\item HOMER Pro do not have a explicit equipment called charge controller. It uses a controller resource that can perform in two different ways, according of the optimization choice or the user choice: load following or cycle charging~\cite{HOMER}. During the tests it was chosen the load following controller: it produces only enough power to meet the demand~\cite{HOMER};
	\item It was assumed the value of 5\% of capacity shortage that is equivalent to 95\% of availability of the PV system. By definition, availability is the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable;
	\item It was assumed a string of two batteries in order to match the voltage of the system of $24$ V DC that was used for the automated synthesis tool;
	\item The premise adopted when using HOMER Pro it was that the user does not know the optimal solution, and that in order to obtain this solution is necessary to include (at the design phase of the tool) generic PV and batteries modules that HOMER Pro will search for the optimized power of each component. With that in mind, it was included a generic flat plate PV of $1$ kW and generic lead-acid batteries of $1$ kW as well (and with capacity of $83.4$ Ah according with HOMER Pro modeling). HOMER, during run-time, decides the size in kW of each module, based on feasibility and lower cost.
\end{itemize}
